% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Present}   {Sr. Mgr. Data Engineering | Senior Developer}{Optum}{Austin}
    {March 2018} {
    				  Leading the platform foundation team which is tasked with the responsibility of building the Spark \& AWS based platform for running the Optum Analytics products.
                      \begin{itemize}
                        \item Lead a team of six senior developers and migrated the OADW pipeline from Oracle to Bigdata
                       	\item Reduced the build time from days in Oracle to less than three hours in Spark
                       	\item Implemented JSQLParser based library for converting one schema into another e.g. Hive to Oracle, Oracle to Hive, etc.
                       	\item Re-wrote dozens of complicated Oracle ETLs in Spark dataframe API
                       	\item Implemented healthcare measures like immunization compliance, ED revisits as ETLs using Spark dataframe API
                       	\item Decoupled application development from schema management by introducing schema-as-contract pattern 
                       	\item Implemented Spark based data-importer with support for overriding partitions \& data types
                        \item Currently working on building the framework for running Optum Analytics applications in AWS  
                        \item Reduced AWS cost by switching to ephemeral EMR with spot fleet for running the builds 
                       	\item Analyzed historic on-prem builds for deciding the optimal spot fleet configuration
                       	\item Worked with the team in implementing StepFunctions based orchestration that spans activities running in AWS as well as in on-prem HDP cluster\\ 
                      \end{itemize}
                    }
                    {Scala,Python,Spark,Hive,Oracle,Hadoop,Maven,Jenkins,HDP,AWS,SNS,SQS,Lambda,StepFunctions,Athena,Glue,Terraform}
  \emptySeparator
  \experience
    {March 2018} {Senior Software Engineer}{The Advisory Board Company}{Austin}
    {October 2015}    
    			 {
    	              Big Data Platform(\textbf{BDP}) is The Advisory Board's first BigData \& AWS based data ingestion pipeline. The objective of the platform is to enable other product teams to build their enrichments against the ingested data. 
    	              \begin{itemize}
    	              	\item Implemented member configuration orchestration using AWS SQS, SNS, Lambda, Step Functions \& python scripts                           
    	              	\item Added support for running industry standard MS \& 3M APR DRG groupers as Spark jobs against AWS EMR                        
    	              	\item Implemented custom Hive authenticator for supporting LDAP  authentication  
    	              	\item Implemented healthcare metrics like percentage readmission, cost \& charges as Spark based enrichments                
    	              	\item Successfully migrated SQL Server based pipeline onto AWS \& BigData stack\\
    	              \end{itemize}
                  }
              {Scala,Java,Spark,Hive,Postgres,S3,SQS,SNS,StepFunctions,Lambda,CloudFormation,EC2,VPC,EMR,Zeppelin}
  \emptySeparator
  \experience
    {June 2015}     {Associate Development Manager}{The Advisory Board Company}{Chennai}
    {Sep 2013}    {
    	              PDR is a centralized large-scale multi-tenant patient data repository. It supports functionalities like loading of data in real-time, restful endpoints for querying loaded data and other patient data related analytics.
                      \begin{itemize}
                        \item Used T4 templates for automated generation of .Net code from XML files
                        \item Implemented PowerShell based framework for end-to-end testing of the application
                        \item Implemented multi-threaded worker engine for processing SQL Server Service broker queues
                        \item Interfaced with the team in the USA \& managed the development \& services team in India\\
                      \end{itemize}
                    }
                    {C\#,SQL Server,WPF,Asp.Net WebApi,Rx .Net,PowerShell,xUnit,Ninject}
  \emptySeparator
  \experience
  {August 2013}     {Analyst}{Barclays Capital}{Pune}
  {July 2012}   	{
  					  Worked on two applications: Meteor \& CDRP. Meteor is a trade capture tool used for precious and base metal trading. CDRP is a commodities specific in-house
  					  developed risk calculation engine used for calculating risk of vanilla and exotic trades.
                      \begin{itemize}
                        \item Implemented web based frontend for the application. Focused on application performance related issues.
                        \item Implemented WIX based installers.\\
                      \end{itemize}
                    }
                    {C\#,Asp.Net,jQuery,Bootstrap,WPF,WIX,SQL Server}
  \emptySeparator         
  \experience
  {June 2012}  {Senior Software Engineer}{The Advisory Board Company}{Chennai}
  {August 2010}   {
                      Worked on market leading analytics software called Crimson Continuum Care. It offers severity-adjusted performance profiles, enabling the hospital–physician collaboration needed to advance quality goals and secure cost savings.  
                      \begin{itemize}
                        \item Part of the product architecture review committee
                        \item Re-wrote measure mapping engine. Improved overall performance by significantly reducing number of database hits
                        \item Re-architectured PDF reporting module to support unlimited number of reports
                        \item Implemented TPL based in-memory measure calculation engine called Insight\\  
                      \end{itemize}
                  }
                  {C\#,Asp.Net MVC,jQuery,SQL Server,Mercurial,.Net TPL} 
  \emptySeparator         
  \experience
  {July 2010}  {Senior System Engineer}{Infosys Technologies Ltd.}{Bangalore}
  {October 2007}   {
				  	\begin{itemize}                                         
				  		\item Successfully migrated applications running on commercial workflow engine over to WF 3.0 platform.
				  		\item Single-handedly built web app called Vendor Portal using WF 3.0, Asp.Net, jQuery, Ajax.
				  		\item Received awards \& accolades for introducing new technologies \& good software development practices in the team(s).\\
				  	\end{itemize}
				  }
  				  {C\#,Asp.Net,Ajax,WF 3.0,jQuery,SQL Server}
\end{experiences}
